A Generic and Efficient E-field Parallel Imaging Correlator for Next-Generation Radio Telescopes

### 2016-08-22 imaging_demo/ms.tex
Minor changes
From 5c6f2b0 (mnras):
====================

In ms.tex,

(*) Minor changes throughout

In epic.bib,

(*) Add references to holography papers

This can be equivalently re-written as:
\begin{align}\label{eqn:software-holography}
  V_{ab}(f,t) &= \int B_{ab}(\mathbf{r}_{ab}-\mathbf{r},f,t) \nonumber\\ 
              &\qquad \times \left[\int I(\hat{\mathbf{s}},f,t)\,e^{-2\pi i f\mathbf{r}.\hat{\mathbf{s}}/c}\,\dif\Omega\right]\dif^2\mathbf{r}\,+\, n_{ab}(f,t),
\end{align}
where, $B_{ab}(\mathbf{r},f,t)$ denotes the {\bf power response of the antenna pair obtained in the measurement plane} by a spatial Fourier transform of $\mathcal{B}_{ab}(\hat{\mathbf{s}},f,t)$. Effectively, the multiplication in image space by $\mathcal{B}_{ab}(\hat{\mathbf{s}},f,t)$ has been replaced by a convolution with $B_{ab}(\mathbf{r},f,t)$ in {\bf measurement plane}. This is the software holographic equivalent of a traditional FX correlator output.

@@

We have implemented the MOFF imaging technique in our ``E-field Parallel Imaging
Correlator'' -- a highly parallelized Object Oriented Python 
package,\footnote{The E-field Parallel Imaging Correlator (EPIC) package can be 
accessed at https://github.com/nithyanandan/EPIC} now publicly available. Besides 
implementing the MOFF imaging algorithm it also includes visibility-based imaging 
using the software holography technique and a simulator for generating electric 
fields from a sky model.

@@

{\bf For a heterogeneous array, it is necessary to keep track of antennas and antenna pairs of different types which will determine the final weighting in the synthesized image.} We consider a heterogeneous array consisting of a total of $\Nant$ antennas under $N_\textrm{T}$ different types. And under each antenna type $i$, there are $n_i$ antennas such that $\sum_i n_i = \Nant$. The total number of unique non-zero spacing antenna pairs is $\Nant(\Nant-1)/2$ and there are potentially up to $N_\textrm{T}(N_\textrm{T}+1)/2$ unique antenna pair types obtained by pairwise combination of the $N_\textrm{T}$ antenna types. Thus, the total number of antenna pairs, 
\begin{align}\label{eqn:total-baselines}
  \frac{1}{2}\Nant(\Nant-1) &= \frac{1}{2}\,\sum_{ij} n_{ij}, \\
  \textrm{where}, \quad   n_{ij} &= \begin{cases}
    n_i\,n_j & i\ne i \\
    n_i(n_i-1) & i=j, 
  \end{cases}
\end{align}
is obtained by counting antenna pairs, $n_{ij}$, in different antenna pair types, $ij$.

Since equation~\ref{eqn:wt-dirty-image-EPIC} is obtained by averaging weighted fringes over all unique antenna pairs, it can be expressed as: 
\begin{align}\label{eqn:wt-dirty-image-EPIC-decomp}
  \mathcal{I}^\prime &= \frac{1/2}{\Nant(\Nant-1)/2}\,\sum_{ij}\sum_{\substack{ab\\a\ne b\\a\in i, b\in j}}\,\mathcal{I}^\prime_{ab}
\end{align}
Here, equation~\ref{eqn:wt-dirty-image-EPIC} has been decomposed as the sum of fringes over all unique antenna pairs in an antenna pair type (innermost summation) and subsequently summed over all antenna pair types.

{\bf For purposes of demonstration in this study, we make the following simplification.} We assume that the spatial distribution of antenna pairs in each antenna pair type are similar and thus result in a similar dirty image, $\mathcal{I}_\textrm{D}^\textrm{iso}$. This usually holds when $\Nant$ is large and antennas under each antenna type are chosen randomly such that differences in the point spread functions are insignificant. Under this assumption, equation~\ref{eqn:wt-dirty-image-EPIC-decomp} can be written as:
\begin{align}\label{eqn:wt-dirty-image-EPIC-decomp-approx1}
  \mathcal{I}^\prime &\approx \frac{\mathcal{I}_\textrm{D}^\textrm{iso}}{\Nant(\Nant-1)}\,\sum_{ij}\sum_{\substack{ab\\a\ne b\\a\in i, b\in j}} \mathcal{W}^{\textrm{G}\star}_a\,\mathcal{W}^\textrm{G}_b\,\mathcal{W}^\textrm{I}_a\,\mathcal{W}^{\textrm{I}\star}_b,
\end{align}
where, $\mathcal{I}_\textrm{D}^\textrm{iso}$ is approximately the same for all terms and has been pulled outside the summations. For all antennas indexed by $a$ that belong to a particular type $i$, we replace $\mathcal{W}_a$ with $\mathcal{W}_{(i)}$ {\bf and is applicable to those arising} from both instrumental (superscript `$I$') and gridding (superscript `$G$') origins. Using arguments similar to those in equation~\ref{eqn:total-baselines}, equation~\ref{eqn:wt-dirty-image-EPIC-decomp-approx1} can be further simplified to:
\begin{align}\label{eqn:wt-dirty-image-EPIC-decomp-approx2}
  \mathcal{I}^\prime &\approx \frac{\mathcal{I}_\textrm{D}^\textrm{iso}}{\Nant(\Nant-1)}\,\sum_{ij}n_{ij}\,\mathcal{W}^{\textrm{G}\star}_{(i)}\,\mathcal{W}^\textrm{G}_{(j)}\,\mathcal{W}^\textrm{I}_{(i)}\,\mathcal{W}^{\textrm{I}\star}_{(j)}.
\end{align}
Then the effective attenuation of the dirty image due to instrumental and gridding weights is:
\begin{align}\label{eqn:effective-weighting}
  \mathcal{W}_\textrm{eff} &= \mathcal{I}^\prime\, / \,\mathcal{I}_\textrm{D}^\textrm{iso}.
\end{align}
This means that the effective attenuation of the dirty image is obtained by combinations of the fourth power of antenna voltage patterns each weighted by the number of antenna pairs in those antenna pair types. In an optimally weighted image, $\mathcal{W}^\textrm{G}_{(i)} \equiv \mathcal{W}^\textrm{I}_{(i)}$ and thus, equation~\ref{eqn:effective-weighting} reduces to:
\begin{align}\label{eqn:effective-weighting-optimal}
  \mathcal{W}_\textrm{eff}^\textrm{opt} &\approx \frac{1}{\Nant(\Nant-1)}\,\sum_{ij} n_{ij}\,\left|\mathcal{W}^\textrm{I}_{(i)}\right|^2\left|\mathcal{W}^\textrm{I}_{(j)}\right|^2,
\end{align}
where the superscript `$\textrm{opt}$' denotes `optimal'.

For purposes of illustration, we consider a simple scenario in which there are two antenna types each containing roughly equal numbers of antennas with similar layouts but the analysis is performed under the wrong assumption that all antennas are identical and are all of the first type. In an optimally weighted image, the optimal effective weighting given by equation~\ref{eqn:effective-weighting-optimal} will be:
\begin{align}\label{eqn:effective-weighting-optimal-example}
  \mathcal{W}_\textrm{eff}^\textrm{opt} &\approx \frac{1}{\Nant(\Nant-1)}\,\left[n_1(n_1-1)\,\left|\mathcal{W}^\textrm{I}_{(1)}\right|^4 \right.\nonumber\\
  &\qquad\qquad\qquad\qquad + n_2(n_2-1)\,\left|\mathcal{W}^\textrm{I}_{(2)}\right|^4 \nonumber\\
  &\qquad\qquad\qquad\qquad \left. + n_1n_2\,\left|\mathcal{W}^\textrm{I}_{(1)}\right|^2\,\left|\mathcal{W}^\textrm{I}_{(2)}\right|^2\right].
\end{align}
On the other hand, $\mathcal{W}^\textrm{G}_{(1)} = \mathcal{W}^\textrm{I}_{(1)}$ and $\mathcal{W}^\textrm{G}_{(2)} = \mathcal{W}^\textrm{I}_{(1)}$ for an image obtained in the erroneous case in which all antennas are assumed to be identical. It will be sub-optimal with effective weighting:
\begin{align}\label{eqn:effective-weighting-optimal-example}
  \mathcal{W}_\textrm{eff}^\textrm{sub} &\approx \frac{1}{\Nant(\Nant-1)}\,\left[n_1(n_1-1)\,\left|\mathcal{W}^\textrm{I}_{(1)}\right|^4\right.\nonumber\\
  &\qquad\qquad\qquad\qquad + n_2(n_2-1)\,\left|\mathcal{W}^\textrm{I}_{(1)}\right|^2\,\left|\mathcal{W}^\textrm{I}_{(2)}\right|^2 \nonumber\\
  &\qquad\qquad\qquad\qquad \left. + n_1n_2\,\left|\mathcal{W}^\textrm{I}_{(1)}\right|^2 \,\mathcal{W}^\textrm{I}_{(1)}\,\mathcal{W}^{\textrm{I}\star}_{(2)}\right].
\end{align}
Finally, since no {\it a priori} information will be available about the heterogeneous array in case of the erroneous assumption, the effective weighting in the image will be believed to be $\mathcal{W}_\textrm{eff}^\textrm{err} = \left|\mathcal{W}_{(1)}^\textrm{I}\right|^4$.

@@

\begin{figure*}
\subfloat[][Optimally weighted EPIC image]{\label{fig:nonphysical-image}\includegraphics[width=0.5\linewidth]{figure10a.eps}}
\subfloat[][Estimates of normalized radial flux density profile]{\label{fig:norm-flux-density}\includegraphics[width=0.42\linewidth]{figure10b.eps}}
\caption{(a)~Optimally weighted image, $\mathcal{I}^\prime$, of simulated sky model obtained by EPIC using MOFF algorithm after averaging over entire bandwidth and duration of simulated observation. 51 antennas in the inner core of the MWA layout were used with uniformly illuminated square apertures. Roughly half of them were squares with 1.1~m sides (first type) and the rest with 6.6~m (second type). Point sources were simulated along westward and south-westward directions with random flux densities brighter than 10~Jy. Black boxes shown around point sources are for purposes of collecting image statistics. (b)~Normalized flux density estimates, $\widehat{\mathcal{I}}_\textrm{M}^\textrm{norm}$, as a function of distance from image center. Bands indicate an approximate ``$1\sigma$'' uncertainty arising from sidelobe confusion and intrinsic randomness of electric fields simulated for point sources in the sky model. Gray and red bands correspond to optimal and erroneous cases respectively, where in the latter, all antennas were erroneously assumed to be identical and of the first type. The dashed and solid line styles correspond to point sources in the westward and south-westward directions respectively. In the optimal case, the normalized estimates are consistent with unity to within ``$1\sigma$'' in almost all regions of the image, whereas in the erroneous case, they are mis-estimated (underestimated) with high significance ($\gtrsim 5\sigma$) in most regions of the image. There is no significant difference in estimates between the two different directions of point sources studied.}
\label{fig:versatility}
\end{figure*}

@@

\begin{table}
  \scriptsize
  \centering
  \caption{Radio telescopes and array layouts.}
  \label{tab:antenna-layouts}
  \begin{threeparttable}
  \begin{tabular}{ccccc} 
    \hline
    Telescope & Core & Number & Antenna & Frequency \\
              & size & of Antennas & size & \\
              & $b_\textrm{max}$ (in m) & $\Nant$ & $A_\textrm{a}$ (in m$^2$) & $f_0$ (in MHz) \\
    \hline
    MWA-112\tnote{a} & 1400 & 112 & 16 & 150 \\
    MWA-240\tnote{a} & 1400 & 240 & 16 & 150 \\
    MWA-496\tnote{a} & 1400 & 496 & 16 & 150 \\
    MWA-112\tnote{a} & 1400 & 1008 & 16 & 150 \\
    LOFAR-LC\tnote{b} & 3500 & 24 & 5809 & 50 \\
    LOFAR-HC\tnote{b} & 3500 & 48 & 745 & 150 \\
    LWA1 & 100 & 256 & 10 & 50 \\
    LWA-OV\tnote{c} & 200 & 256 & 10 & 50 \\
    HERA-19 & 70 & 19 & 154 & 150 \\
    HERA-37 & 98 & 37 & 154 & 150 \\
    HERA-331 & 294 & 331 & 154 & 150 \\
    HERA-6769\tnote{d} & 1330 & 6769 & 154 & 150 \\
    SKA1-LC\tnote{e} & 1000 & 750 & 962 & 150 \\
    SKA1-LCD\tnote{f} & 1000 & 192,000 & 2 & 150 \\
    CHIME & 100 & 1280 & 8 & 600 \\
    HIRAX\tnote{g} & 200 & 1024 & 28 & 600 \\
    \hline
  \end{tabular}
  \begin{tablenotes}
    \item[a] MWA-N denotes N tiles in the specified core diameter
    \item[b] LC and HC denotes low band and high band stations inside the 
      specified core diameter 
    \item[c] Owens Valley LWA
    \item[d] Hypothetically chosen to have a total collecting area of 
      1~km$^2$
    \item[e] This is the number of beamformed stations expected to be in the 
      core, roughly three-fourths of the total number
    \item[f] All dipoles inside the core are used as independent elements 
      without station beamforming
    \item[g] Hydrogen Intensity mapping and Real-time Analysis eXperiment
  \end{tablenotes}
  \end{threeparttable}
\end{table}

>>>>

This can be equivalently re-written as:
\begin{align}\label{eqn:software-holography}
  V_{ab}(f,t) &= \int B_{ab}(\mathbf{r}_{ab}-\mathbf{r},f,t) \nonumber\\ 
              &\qquad \times \left[\int I(\hat{\mathbf{s}},f,t)\,e^{-2\pi i f\mathbf{r}.\hat{\mathbf{s}}/c}\,\dif\Omega\right]\dif^2\mathbf{r}\,+\, n_{ab}(f,t),
\end{align}
where, $B_{ab}(\mathbf{r},f,t)$ denotes the {\bf power response of the antenna pair obtained in the measurement plane} by a spatial Fourier transform of $\mathcal{B}_{ab}(\hat{\mathbf{s}},f,t)$. Effectively, the multiplication in image space by $\mathcal{B}_{ab}(\hat{\mathbf{s}},f,t)$ has been replaced by a convolution with $B_{ab}(\mathbf{r},f,t)$ in {\bf measurement plane}. This is the software holographic equivalent of a traditional FX correlator output. {\bf For context, the term ``holography'' is derived from holographic measurements of the complex antenna aperture illumination pattern \citep{ben76,sco77}. In the present context, ``software holography'' refers to the application of this antenna aperture illumination pattern in software for imaging.}

@@

We have implemented the MOFF imaging technique in our ``E-field Parallel Imaging Correlator'' -- a highly parallelized Object Oriented Python package,\footnote{The E-field Parallel Imaging Correlator (EPIC) package can be accessed at https://github.com/nithyanandan/EPIC} now publicly available. Besides implementing the MOFF imaging algorithm it also includes {\bf a simulator for generating electric fields from a sky model and a visibility-based imaging using the software holography technique.}

@@

{\bf For a heterogeneous array, it is necessary to keep track of antennas and antenna pairs of different types which will determine the final weighting in the synthesized image.} We consider a heterogeneous array consisting of a total of $\Nant$ antennas under $N_\textrm{T}$ different types. And under each antenna type $i$, there are $n_i$ antennas such that $\sum_i n_i = \Nant$. The total number of unique non-zero spacing antenna pairs is $\Nant(\Nant-1)/2$ and there are potentially up to $N_\textrm{T}(N_\textrm{T}+1)/2$ unique antenna pair types obtained by pairwise combination of the $N_\textrm{T}$ antenna types. Thus, the total number of antenna pairs, 
\begin{align}\label{eqn:total-baselines}
  \frac{1}{2}\Nant(\Nant-1) &= \frac{1}{2}\,\sum_{ij} n_{ij}, \\
  \textrm{where}, \quad   n_{ij} &= \begin{cases}
    n_i\,n_j, & i\ne i \\
    n_i(n_i-1), & i=j, 
  \end{cases}
\end{align}
is obtained by counting antenna pairs, $n_{ij}$, in different antenna pair types, $ij$.

Since equation~\ref{eqn:wt-dirty-image-EPIC} is obtained by averaging weighted fringes over all unique antenna pairs, it can be expressed as: 
\begin{align}\label{eqn:wt-dirty-image-EPIC-decomp}
  \mathcal{I}^\prime &= \frac{1/2}{\Nant(\Nant-1)/2}\,\sum_{ij}\sum_{\substack{ab\\a\ne b\\a\in i, b\in j}}\,\mathcal{I}^\prime_{ab}
\end{align}
Here, equation~\ref{eqn:wt-dirty-image-EPIC} has been decomposed as the sum of fringes over all unique antenna pairs in an antenna pair type (inner sum) and subsequently summed over all antenna pair types (outer sum).

For purposes of demonstration in this study, we make the following simplification. We assume that the spatial distribution of antenna pairs in each antenna pair type are similar and thus result in a similar dirty image, $\mathcal{I}_\textrm{D}^\textrm{iso}$. This usually holds when $\Nant$ is large and antennas under each antenna type are chosen randomly such that differences in the point spread functions are insignificant. Under this assumption, equation~\ref{eqn:wt-dirty-image-EPIC-decomp} can be written as:
\begin{align}\label{eqn:wt-dirty-image-EPIC-decomp-approx1}
  \mathcal{I}^\prime &\approx \frac{\mathcal{I}_\textrm{D}^\textrm{iso}}{\Nant(\Nant-1)}\,\sum_{ij}\sum_{\substack{ab\\a\ne b\\a\in i, b\in j}} \mathcal{W}^{\textrm{G}\star}_a\,\mathcal{W}^\textrm{G}_b\,\mathcal{W}^\textrm{I}_a\,\mathcal{W}^{\textrm{I}\star}_b,
\end{align}
where, $\mathcal{I}_\textrm{D}^\textrm{iso}$ is approximately the same for all terms and has been pulled outside the summations. For all antennas indexed by $a$ that belong to a particular type $i$, we replace $\mathcal{W}_a$ with $\mathcal{W}_{(i)}$ {\bf and is applicable to those arising} from both instrumental (superscript `$I$') and gridding (superscript `$G$') origins. Using arguments similar to those in equation~\ref{eqn:total-baselines}, equation~\ref{eqn:wt-dirty-image-EPIC-decomp-approx1} can be further simplified to:
\begin{align}\label{eqn:wt-dirty-image-EPIC-decomp-approx2}
  \mathcal{I}^\prime &\approx \frac{\mathcal{I}_\textrm{D}^\textrm{iso}}{\Nant(\Nant-1)}\,\sum_{ij}n_{ij}\,\mathcal{W}^{\textrm{G}\star}_{(i)}\,\mathcal{W}^\textrm{G}_{(j)}\,\mathcal{W}^\textrm{I}_{(i)}\,\mathcal{W}^{\textrm{I}\star}_{(j)}.
\end{align}
Then the effective attenuation of the dirty image due to instrumental and gridding weights is:
\begin{align}\label{eqn:effective-weighting}
  \mathcal{W}_\textrm{eff} &= \mathcal{I}^\prime\, / \,\mathcal{I}_\textrm{D}^\textrm{iso}.
\end{align}
This means that the effective attenuation of the dirty image is obtained by combinations of the fourth power of antenna voltage patterns each weighted by the number of antenna pairs in those antenna pair types. In an optimally weighted image, $\mathcal{W}^\textrm{G}_{(i)} \equiv \mathcal{W}^\textrm{I}_{(i)}$ and thus, equation~\ref{eqn:effective-weighting} reduces to:
\begin{align}\label{eqn:effective-weighting-optimal}
  \mathcal{W}_\textrm{eff}^\textrm{opt} &\approx \frac{1}{\Nant(\Nant-1)}\,\sum_{ij} n_{ij}\,\left|\mathcal{W}^\textrm{I}_{(i)}\right|^2\left|\mathcal{W}^\textrm{I}_{(j)}\right|^2,
\end{align}
where the superscript `$\textrm{opt}$' denotes `optimal'.

For purposes of illustration, we consider a simple scenario in which there are two antenna types each containing roughly equal numbers of antennas with similar layouts but the analysis is performed under the wrong assumption that all antennas are identical and are all of the first type. In an optimally weighted image, the optimal effective weighting given by equation~\ref{eqn:effective-weighting-optimal} will be:
\begin{align}\label{eqn:effective-weighting-optimal-example}
  \mathcal{W}_\textrm{eff}^\textrm{opt} &\approx \frac{1}{\Nant(\Nant-1)}\,\left[n_1(n_1-1)\,\left|\mathcal{W}^\textrm{I}_{(1)}\right|^4 \right.\nonumber\\
  &\qquad\qquad\qquad\qquad + n_2(n_2-1)\,\left|\mathcal{W}^\textrm{I}_{(2)}\right|^4 \nonumber\\
  &\qquad\qquad\qquad\qquad \left. + n_1n_2\,\left|\mathcal{W}^\textrm{I}_{(1)}\right|^2\,\left|\mathcal{W}^\textrm{I}_{(2)}\right|^2\right].
\end{align}
On the other hand, $\mathcal{W}^\textrm{G}_{(1)} = \mathcal{W}^\textrm{I}_{(1)}$ and $\mathcal{W}^\textrm{G}_{(2)} = \mathcal{W}^\textrm{I}_{(1)}$ for an image obtained in the erroneous case in which all antennas are assumed to be identical. It will be sub-optimal with effective weighting:
\begin{align}\label{eqn:effective-weighting-suboptimal-example}
  \mathcal{W}_\textrm{eff}^\textrm{sub} &\approx \frac{1}{\Nant(\Nant-1)}\,\left[n_1(n_1-1)\,\left|\mathcal{W}^\textrm{I}_{(1)}\right|^4\right.\nonumber\\
  &\qquad\qquad\qquad\qquad + n_2(n_2-1)\,\left|\mathcal{W}^\textrm{I}_{(1)}\right|^2\,\left|\mathcal{W}^\textrm{I}_{(2)}\right|^2 \nonumber\\
  &\qquad\qquad\qquad\qquad \left. + n_1n_2\,\left|\mathcal{W}^\textrm{I}_{(1)}\right|^2 \,\mathcal{W}^\textrm{I}_{(1)}\,\mathcal{W}^{\textrm{I}\star}_{(2)}\right].
\end{align}
Finally, since no {\it a priori} information will be available about the heterogeneous array in case of the erroneous assumption, the effective weighting in the image will be believed to be $\mathcal{W}_\textrm{eff}^\textrm{err} = \left|\mathcal{W}_{(1)}^\textrm{I}\right|^4$.

@@

\begin{figure*}
\subfloat[][Optimally weighted EPIC image]{\label{fig:nonphysical-image}\includegraphics[width=0.5\linewidth]{figure10a.eps}}
\subfloat[][Estimates of normalized radial flux density profile]{\label{fig:norm-flux-density}\includegraphics[width=0.42\linewidth]{figure10b.eps}}
\caption{{\bf (a)~Optimally weighted image, $\mathcal{I}^\prime$, of simulated sky model obtained by EPIC using MOFF algorithm after averaging over entire bandwidth and duration of simulated observation. 51 antennas in the inner core of the MWA layout were used with uniformly illuminated square apertures. Roughly half of them were squares with 1.1~m sides (first type) and the rest with 6.6~m (second type). Point sources were simulated along westward and south-westward directions with random flux densities brighter than 10~Jy. Black boxes shown around point sources are for purposes of collecting image statistics. (b)~Normalized flux density estimates, $\widehat{\mathcal{I}}_\textrm{M}^\textrm{norm}$, as a function of distance from image center. Bands indicate an approximate ``$1\sigma$'' uncertainty arising from sidelobe confusion and intrinsic randomness of electric fields simulated for point sources in the sky model. Gray and red bands correspond to optimal and erroneous cases respectively, where in the latter, all antennas were erroneously assumed to be identical and of the first type. The dashed and solid line styles correspond to point sources in the westward and south-westward directions respectively. In the optimal case, the normalized estimates are consistent with unity to within ``$1\sigma$'' in almost all regions of the image, whereas in the erroneous case, they are mis-estimated (underestimated) with high significance ($\gtrsim 5\sigma$) in most regions of the image. There is no significant difference in estimates between the two different directions of point sources studied.}}
\label{fig:versatility}
\end{figure*}

@@

\begin{table}
  \scriptsize
  \centering
  \caption{Radio telescopes and array layouts.}
  \label{tab:antenna-layouts}
  \begin{threeparttable}
  \begin{tabular}{ccccc} 
    \hline
    Telescope & Core & Number of & Antenna & Frequency \\
              & size & Antennas & size & \\
              & $b_\textrm{max}$ (m) & $\Nant$ & $A_\textrm{a}$ (m$^2$) & $f_0$ (MHz) \\
    \hline
    MWA-112\tnote{a} & 1400 & 112 & 16 & 150 \\
    MWA-240\tnote{a} & 1400 & 240 & 16 & 150 \\
    MWA-496\tnote{a} & 1400 & 496 & 16 & 150 \\
    MWA-112\tnote{a} & 1400 & 1008 & 16 & 150 \\
    LOFAR-LC\tnote{b} & 3500 & 24 & 5809 & 50 \\
    LOFAR-HC\tnote{b} & 3500 & 48 & 745 & 150 \\
    LWA1 & 100 & 256 & 10 & 50 \\
    LWA-OV\tnote{c} & 200 & 256 & 10 & 50 \\
    HERA-19 & 70 & 19 & 154 & 150 \\
    HERA-37 & 98 & 37 & 154 & 150 \\
    HERA-331 & 294 & 331 & 154 & 150 \\
    HERA-6769\tnote{d} & 1330 & 6769 & 154 & 150 \\
    SKA1-LC\tnote{e} & 1000 & 750 & 962 & 150 \\
    SKA1-LCD\tnote{f} & 1000 & 192,000 & 2 & 150 \\
    CHIME & 100 & 1280 & 8 & 600 \\
    HIRAX\tnote{g} & 200 & 1024 & 28 & 600 \\
    \hline
  \end{tabular}
  \begin{tablenotes}
    \item[a] MWA-N denotes N tiles in the specified core diameter
    \item[b] LC and HC denotes low band and high band stations inside the 
      specified core diameter 
    \item[c] Owens Valley LWA
    \item[d] Hypothetically chosen to have a total collecting area of 
      1~km$^2$
    \item[e] This is the number of beamformed stations expected to be in the 
      core, roughly three-fourths of the total number
    \item[f] All dipoles inside the core are used as independent elements 
      without station beamforming
    \item[g] Hydrogen Intensity mapping and Real-time Analysis eXperiment
  \end{tablenotes}
  \end{threeparttable}
\end{table}
